# Title: **Identifications and Solutions for the Aging Workforce in Malaysia**

### **Group Members:**
```{r echo = FALSE, results = 'asis'}
name1 <- c('Wong Jia Hui', 'S2192852')
name2 <- c('Danial Mirza Bin Madrawi', '22062607')
name3 <- c('Low Boon Kiat', '17138399')
name4 <- c('Hongsheng Jie', '22064728')
name5 <- c('Yuejing Huang', 'S2158553')
row_names <- c(1:5)
col_names <- c('Names', 'Matric ID')
member_df <- data.frame(matrix(c(name1, name2, name3, name4, name5), 5, 2, byrow = TRUE, dimnames = list(row_names, col_names)))
library(knitr)
kable(member_df)
```
### **Introduction**
According to a report from United Nations (UN) in 2015, the world is moving towards an aging population. The number of elderly population is estimated to reach 1.4 billion by 2030 and 2.1 billion by 2050. The ageing of the world's population is the result of decline in birth rate and increased life expectancy due to better health facilities which have changed the demographic trends across the global. One of the major impacts faced by the organisation and governments will be aging workforce. Organisation and governments are required to make adjustment on the existing infrastructure and policies to meet the needs of aging workforce trends.

This project focuses on identifying the trends of aging workforce in Malaysia and discusses how Malaysia could address the challenges arise from aging workforce based on the collected time-series data starting from year 1982 to year 2021. A predictive model will also be proposed for predicting the unemployment rate and growth rate of aging workforce in Malaysia.

### **Objective**
The objectives of this project are:-

1. To identify trends of aging workforce in Malaysia.
2. To propose mitigation measures to address aging workforce challenges.
3. To develop a predictive model for predicting unemployment rate and growth rate of aging workforce.

### **Methodology**
1. Define Problem: The problem from this project is defined. To prove the labor force of Malaysia is aging using Population Dataset.
2. Data Procurement: The data sources were obtained from Ministry of Statistics Malaysia website. 
3. Data Understanding: Finding the existence of null value, the definition of each columns.
4. Data Preparation: Concatinating multiple sources into one, change the intital columns' names into more understandatble names. Separate labour force by age groups and genders. Convert age columns into numeric columns 
5. Data Cleaning: Null values were replaced with value using Linear Model. The data now void from any null value.
6. Exploratory Data Analysis: Using the data, descriptive and visual analysis of the data was done to uncover patterns, trends, relationships, and insights. You may also use statistical tests and hypothesis testing to validate your findings.
7. Modeling: This is where you apply various machine learning or statistical techniques to build predictive or explanatory models based on the data. You should also evaluate the performance and accuracy of your models using appropriate metrics and methods.
8. Results and Discussion: This is where you communicate your findings and recommendations to the stakeholders or audience. You should also discuss the limitations and assumptions of your analysis, as well as any future steps or improvements that can be made.

### **Data Understanding**
During Data Understanding phase, raw data is identified, collected and analyzed for the usage of this project

**1. Raw Data**  
All the raw data sets are downloaded from https://www.dosm.gov.my/portal-main/time-series  
A total of five (5) different raw data sets are used in this project, as listed below:-

* Under category of Malaysia Economic Statistics - Time Series 2019  
    + No.19 - Population  
    
* Under category of  Labour Force Survery (LFS) Time Series Statistics by State, 1982 - 2021  
    + No.1 - Employed persons by age group, Malaysia/states
    + No.9 - Labour force by age group, Malaysia/states
    + No.18 - Principal statistics of the labour force by sex, Malaysia
    
Since multiple raw datasets are acquired, data extraction and data integration is required to process the raw datasets into a clean dataset for data analysis and to train the predictive model.

**2. Data Description**

The description of each raw data sets collected is shown in the table below:-

|Name of Raw Dataset|   Description |
|:----------------------------------------------|:-------------------------------------------------|
|No.19 - Population|    It contains data for the population of Malaysia (1892 - 2019), main demographic rates (1911 - 2019), life expectancy at birth by ethnic group and sex (1956 - 2019) and age-specific fertility rate and total fertility rate (1956 - 2019). The interested data for our project usage will be Malaysia population, life expectancy and birth rate|
|No.1 - Employed persons by age group, Malaysia/states|   It contains data on the number of employed person by age group in Malaysia (1982 - 2021)|
|No.9 - Labour force by age group, Malaysia/states|   It contains data on the number of labour force by age group in Malaysia (1982 - 2021)|
|No.18 - Principal statistics of the labour force by sex, Malaysia|   It contains data on the number of labour force and employed person by sex in Malaysia (1982 - 2021)|

**3. Data Quality**

The comments on the data quality of those collected raw data sets are shown below:-

|Name of Raw Dataset|   Comments on Data Quality|
|:----------------------------------------------|:-------------------------------------------------|
|No.19 - Population |   Missing data for year 2020 and year 2021|
|No.1 - Employed persons by age group, Malaysia/states|   Missing data for year 1991 and year 1993|
|No.9 - Labour force by age group, Malaysia/states|   Missing data for year 1991 and year 1993|
|No.18 - Principal statistics of the labour force by sex, Malaysia|   Missing data for year 1991 and year 1993|

Based on the comments, data cleaning is required to fill in the missing values. The process of data cleaning will be discussed in later stage.

### **Data Preparation**
**1. Data Extraction and Selection**
```{r}
# Extract data from raw .xlsx file and create a new dataframe
library(xlsx)
population_df <- read.xlsx("no19.xlsx", sheetIndex = 1, rowIndex = 6:91, colIndex = 1:7)
lifeexp_df <- read.xlsx("no19.xlsx", sheetIndex = 3, rowIndex = 12:66, colIndex = 1:11)
birthrate_df <- read.xlsx("no19.xlsx", sheetIndex = 2, rowIndex = 13:117, colIndex = 1:9)
labour_df <- read.xlsx("no9.xlsx", sheetIndex = 1, rowIndex = 5:43, colIndex = 2:13)
employ_df <- read.xlsx("no1.xlsx", sheetIndex = 1, rowIndex = 5:43, colIndex = 2:13)
malewf_df <- read.xlsx("no18.xlsx", sheetIndex = 1, rowIndex = 8:46, colIndex = 2:9)
femalewf_df <- read.xlsx("no18.xlsx", sheetIndex = 2, rowIndex = 8:46, colIndex = 2:9)

# Rename column names
colnames(population_df) <- c("year", "total", "", "age0-14", "age15-64", "age65+", "avg_apgr")
colnames(lifeexp_df) <- c("year", "m_life", "f_life", "bm_life", "bf_life", "cm_life", "cf_life", "im_life", "if_life", "om_life", "of_life")
colnames(birthrate_df) <- c("year", "cr_naturalincrease", "crude_br", "crude_dr", "total_fr", "neonatal_mr", "infant_mr", "toddler_mr", "maternal_mr")
colnames(labour_df) <- c("year", "total", "age15-19", "age20-24", "age25-29", "age30-34", "age35-39", "age40-44", "age45-49", "age50-54", "age55-59", "age60-64")
colnames(employ_df) <- c("year", "total", "age15-19", "age20-24", "age25-29", "age30-34", "age35-39", "age40-44", "age45-49", "age50-54", "age55-59", "age60-64")
colnames(malewf_df) <-c("year", "m_lf", "m_employed", "m_work<30hrs", "m_unemployed", "m_outside_lf", "participationrate_lf", "unemployment_rate")
colnames(femalewf_df) <-c("year", "f_lf", "f_employed", "f_work<30hrs", "f_unemployed", "f_outside_lf", "participationrate_lf", "unemployment_rate")

# Add new rows with empty data to represent missing year and remove data that do not fall within the year of 1982 - 2021
new_row1 <- population_df[1:2,]
new_row1[] <- NA
population_df <- rbind(population_df, new_row1)
population_df <- population_df[-1:-47,]
population_df$year <- c(1982:2021)

new_row1 <- lifeexp_df[1:2,]
new_row1[] <- NA
lifeexp_df <- rbind(lifeexp_df, new_row1)
lifeexp_df <- lifeexp_df[-1:-16,]
lifeexp_df$year <- c(1982:2021)

new_row1 <- birthrate_df[1:2,]
new_row1[] <- NA
birthrate_df <- rbind(birthrate_df, new_row1)
birthrate_df <- birthrate_df[-1:-66,]
birthrate_df$year <- c(1982:2021)

library(tidyverse)
labour_df <- labour_df %>% add_row(year = 1991, `age15-19` = NA, `age20-24` = NA, `age25-29` = NA, `age30-34` = NA, `age35-39` = NA, `age40-44` = NA, `age45-49` = NA, `age50-54` = NA, `age55-59` = NA, `age60-64` = NA, .before = 10)
labour_df <- labour_df %>% add_row(year = 1994, `age15-19` = NA, `age20-24` = NA, `age25-29` = NA, `age30-34` = NA, `age35-39` = NA, `age40-44` = NA, `age45-49` = NA, `age50-54` = NA, `age55-59` = NA, `age60-64` = NA, .before = 13)

employ_df <- employ_df %>% add_row(year = 1991, `age15-19` = NA, `age20-24` = NA, `age25-29` = NA, `age30-34` = NA, `age35-39` = NA, `age40-44` = NA, `age45-49` = NA, `age50-54` = NA, `age55-59` = NA, `age60-64` = NA, .before = 10)
employ_df <- employ_df %>% add_row(year = 1994, `age15-19` = NA, `age20-24` = NA, `age25-29` = NA, `age30-34` = NA, `age35-39` = NA, `age40-44` = NA, `age45-49` = NA, `age50-54` = NA, `age55-59` = NA, `age60-64` = NA, .before = 13)

malewf_df <- malewf_df %>% add_row(year = 1991, m_lf = NA, m_employed = NA, `m_work<30hrs`= NA, m_unemployed = NA, m_outside_lf = NA, participationrate_lf = NA, unemployment_rate = NA, .before = 10)
malewf_df <- malewf_df %>% add_row(year = 1991, m_lf = NA, m_employed = NA, `m_work<30hrs`= NA, m_unemployed = NA, m_outside_lf = NA, participationrate_lf = NA, unemployment_rate = NA, .before = 13)

femalewf_df <- femalewf_df %>% add_row(year = 1991, f_lf = NA, f_employed = NA, `f_work<30hrs`= NA, f_unemployed = NA, f_outside_lf = NA, participationrate_lf = NA, unemployment_rate = NA, .before = 10)
femalewf_df <- femalewf_df %>% add_row(year = 1991, f_lf = NA, f_employed = NA, `f_work<30hrs`= NA, f_unemployed = NA, f_outside_lf = NA, participationrate_lf = NA, unemployment_rate = NA, .before = 13)

# Filter out the required data for data merging/integration to create a brand new dataset for our project usage
labour_df$`age15-59` <- rowSums(labour_df[,3:11])
employ_df$`age15-59` <- rowSums(employ_df[,3:11])
df <- data.frame(population_df$year, malewf_df$m_lf, femalewf_df$f_lf, malewf_df$m_employed, femalewf_df$f_employed, population_df$`age0-14`, labour_df$`age15-59`, labour_df$`age60-64`, employ_df$`age15-59`, employ_df$`age60-64`, population_df$`age65+`, lifeexp_df$m_life, lifeexp_df$f_life, birthrate_df$crude_br)
colnames(df) <- c('year', 'm_lf', 'f_lf', 'm_employed', 'f_employed', 'age0-14', 'age15-59_lf', 'age60-64_lf', 'age15-59_employ', 'age60-64_employ', 'age65+', 'm_life', 'f_life', 'br')

# Check for data structure and standardize it (if required)
str(df)
df[, c("age0-14", "age65+", "br")] <- lapply(df[, c("age0-14", "age65+", "br")], as.numeric)
str(df)
df[,2:14] <- round(df[,2:14], 2)
```

After the data wrangling process, a **dataset, df** is created and ready for data cleaning process.

The data description is explained in the table below:-

|Column Name|Description|
|:----------------------------------|:---------------------------------|
|year|Year for collected data|
|m_lf|Male labour force (in thousand)|
|f_lf|Female labour force (in thousand)|
|m_employed|Male employed person (in thousand) |
|f_employed|Female employed person (in thousand)|
|age0-14|Population under the age of 0 - 14 (in thousand)|
|age15-59_lf|Labour force under the agoe of 15 - 59 (in thousand)|
|age60-64_lf|Labour force under the age of 60 - 64 (in thousand)|
|age15-59_employ|Employed person under the age of 15 - 59 (in thousand)|
|age60-64_employ|Employed person under the age of 60 -64 (in thousand)|
|age65+|Population above the age of 65|
|m_life|Male life expectancy|
|f_life|Female life expectancy|
|br|Birth rate (in %)|

### **Data Cleaning**
There are 27 NAs in data frame. To impute the NAs, we make use of predict() function to predict each NA based on its neighboring data. First, we make use of for loop iteration and is.na() function to identify NAs. Each time we locate a NA, we create a subset named fit_data which includes two preceding rows and two succeeding rows. The fit_data includes only "year" column and the column with NA as evident by c(1,j). Next, we make use of lm() function to compute a linear model for fit_data. For this linear model, column with NA is outcome variable whereas "year" is predictor variable. Next, we apply predict() function to obtain a predicted value for the NA. 
```{r}
clean_df <- df

# Model-based imputation for missing data
i<-1
j<-1
for (i in 1:nrow(clean_df)){
     for (j in 1:ncol(clean_df)){
         if (is.na(clean_df[i,j])==TRUE){
             fit_data<-clean_df[(i-2):(i+2),c(2,j)]
             model<-lm(unlist(clean_df[(i-2):(i+2),j])~unlist(clean_df[(i-2):(i+2),"year"]),fit_data,na.action=na.exclude)
             new_data<-data.frame(clean_df[(i-2):(i+2),2])
             predicted_data<-predict(model,new_data)
             clean_df[i,j]<-predicted_data[3]
         }else if(i==40){
             break
         }else{
             i=i+1
             j=j+1
         }
     }
}

# Round to 1 decimal place
clean_df[,2:14] <- round(clean_df[,2:14],1)
clean_df
write.csv(clean_df, file="clean-data.csv",row.names=FALSE)
```
### **Exploratory Data Analysis (EDA)**
```{r}
# Load libraries
library("dplyr")
library("ggplot2")
library("reshape2")

# Load files
data = read.csv("clean-data.csv")
# Create DataFrame
df = data.frame(data)
# Check datatypes of DataFrame columns
str(df)
# Summarize DataFame
summary(df)
# Check columns' names 
colnames(df)
# Change columns' names 
colnames(df) = c("Year",
                 "Labour_Force_Male_thousands", 
                 "Labour_Force_Female_thousands", 
                 "Employed_Male_thousands", 
                 "Employed_Female_thousands",
                 "Age_0_to_14_thousands", 
                 "Labour_Force_Age_15_to_59_thousands",
                 "Labour_Force_Age_60_to_64_thousands",
                 "Employed_Age_15_to_59_thousands",
                 "Employed_Age_60_to_64_thousands",
                 "Age_above_65", 
                 "Life_Expectancy_Male",
                 "Life_Expectancy_Female",
                 "Birth_Rate_percentage")
```

**The Total Labour Force in Malaysia has been increasing from 1982 to 2021**

```{r}
# Total Labour Force
df$Labour_Force_Male_thousands+ df$Labour_Force_Female_thousands
# Total Labour Force by Year
ggplot(data = df["Labour_Force_Male_thousands"] + df["Labour_Force_Female_thousands"],
       mapping = aes(x = as.integer(df$Year), 
                     y = Labour_Force_Male_thousands)) +
        geom_point() +
        geom_line() +
        labs(title = "Total Labour Force", subtitle = "Total Labour Force from 1982 to 2021", x = "Years", y = "Total Labour Force")
```

**The Total Employed Labour Force in Malaysia has been increasing from 1982 to 2019 but stagnant since 2020**

```{r}
# Total Employed Labour
ggplot(data = df["Employed_Male_thousands"] + df["Employed_Female_thousands"],
       mapping = aes(x = as.integer(df$Year), 
                     y = Employed_Male_thousands)) +
        geom_point() +
        geom_line() +
        labs(title = "Total Employed Labour", subtitle = "Total Employed Labour from 1982 to 2021", x = "Years", y = "Total Employed Labour")
```

**The Total Umemployed Labour Force in Malaysia has been increasing slowly from 1997 to 2018 but skyrocketed since 2019**

```{r}
# Total Umemployed Labour
ggplot(data = (df["Labour_Force_Male_thousands"] + df["Labour_Force_Female_thousands"])-(df["Employed_Male_thousands"] + df["Employed_Female_thousands"]),
       mapping = aes(x = as.integer(df$Year), 
                     y = Labour_Force_Male_thousands)) +
        geom_point() +
        geom_line()+
        labs(title = "Unemployed Labour", subtitle = "Total of Unemployed Labour from 1982 to 2021", x = "Years", y = "Total Unemployed Labour")
```

**The Total Employed Labour Force in Malaysia aged 15 to 59 has been increasing since 1982 but slow growth of Total Employed Labour Force in Malaysia aged 60 to 64 neticed since 2011**

```{r}
# Total Employed Labor by Group Age
ggplot(data = melt(data = cbind(Year = as.integer(df$Year), df) %>% select(c("Year", "Labour_Force_Age_15_to_59_thousands","Labour_Force_Age_60_to_64_thousands")), id.vars = "Year"),
       mapping = aes(x = Year, 
                     y = value,
                     colour = variable, 
                     group = variable)) +
        geom_point() +
        geom_line()+
        labs(title = "Total Employed Labor by Group Age", subtitle = "Total Employed Labour by Group Age from 1982 to 2021", x = "Years", y = "Total Unemployed Labour")
```
**The Life Expectancy of Female and Male have been incresing since 1982 except for the Male where their Life Expectancy Stagnated sine 2015**

```{r}
# Live Expentancy by Gender
ggplot(data = melt(data = cbind(Year = as.integer(df$Year), df) %>% select(c("Year", "Life_Expectancy_Male", "Life_Expectancy_Female")), id.vars = "Year"),
       mapping = aes(x = Year, 
                     y = value,
                     colour = variable, 
                     group = variable)) +
        geom_point() +
        geom_line()+
        labs(title = "Live Expentancy by Gender", subtitle = "Life Expectancy by Gender from 1982 to 2021", x = "Years", y = "Life Expectancy")
```

**The Total Population in Malaysia has increase since 1982 but the Birth rate of Malaysians has slowly decreasing since 1982**

```{r}
# Total Population VS Birth rate
Total_Population = df['Age_0_to_14_thousands'] + df['Labour_Force_Age_15_to_59_thousands'] + df['Labour_Force_Age_60_to_64_thousands'] + df['Age_above_65']
colnames(Total_Population) = "Total_Population"
cbind(Year = Total_Population/100, df)[c("Year" , "Total_Population", "Birth_Rate_percentage")]
#melt(cbind(Year = Total_Population/100, df)[c("Year" , "Total_Population", "Birth_Rate_percentage")], , id.vars = "Year")
ggplot(data = melt(cbind(Year = Total_Population/100, df)[c("Year" , "Total_Population", "Birth_Rate_percentage")], , id.vars = "Year"),
       mapping = aes(x = Year, 
                     y = value,
                    colour = variable, 
                     group = variable)) +
        geom_point() +
        geom_line()+
        labs(title = "Total Population VS Birth rate", subtitle = "Total Population VS Birth rate from 1982 to 2021", x = "Years")
```

**The Total Malaysian Population age 14 and below slowly increasing unlike huge increase Malaysian age between 15 to 59, there is slow increase of Malaysian age 60 and above**

```{r}
# Malaysia Population by Age Group
Population_by_Age_Group = df[c('Year', 'Age_0_to_14_thousands', 'Labour_Force_Age_15_to_59_thousands', 'Labour_Force_Age_60_to_64_thousands','Age_above_65')]
Population_by_Age_Group
ggplot(data = melt(Population_by_Age_Group, id.vars = "Year"),
       mapping = aes(x = Year, 
                     y = value,
                    fill = variable)) +
        geom_area() +
        labs(title = "Malaysia Population by Age Group", subtitle = "Malaysia Population by Age Group from 1982 to 2021", x = "Years", y = "Total Population")
```
### **Modeling**

{r}
library(randomForest)
data <- read.csv("clean-data.csv")
data <- data.frame(data)

train_indices <- sample(1:nrow(data), size = 0.8 * nrow(data), replace = FALSE)
train_data <- data[train_indices, ]  
test_data <- data[-train_indices, ]

train_data$new <- as.factor(train_data$new)
test_data$new <- as.factor(test_data$new)

model <- randomForest(new ~ ., data = train_data, ntree = 100, mtry = 2, method = "classification")
predictions <- predict(model, newdata = test_data, type = "class")

library(ggplot2)
test_data$Index <- seq_len(nrow(test_data))
plot_data <- rbind(
  data.frame(Index = test_data$Index, Value = test_data$new, Type = "Actual"),
  data.frame(Index = test_data$Index, Value = predictions, Type = "Predicted")
)

ggplot(plot_data, aes(x = Index, y = Value, color = Type, group = Type)) +
  geom_line() +
  geom_point() +
  labs(x = "Index", y = "Value", color = "Type") +
  theme_minimal()
accuracy <- sum(predictions == test_data$new) / length(predictions)
print(paste("Accuracy:", round(accuracy * 100, 2), "%"))


### **Results and Discussion**